%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%--------------------------------------------------------- 
  \cventry
    {Department for Business and Trade} % Job title
    {Senior Data Scientist} % Organization
    {Cardiff, UK} % Location
    {Apr. 2024 - Present} % Date(s)
    {\renewcommand{\labelitemii}{\bullet}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[] {\jobstyle{} 
            \begin{itemize} % Description(s) of tasks/responsibilities
                \item {Delivered rapid crisis response analytics on global containerised trade disruptions, combining Python and SQL expertise to produce timely insights during world events, with clear communication of complex findings to non-technical policy stakeholders.}
                \item {Built end-to-end data infrastructure including a Streamlit dashboard for trend analysis, a graph data model in ArangoDB for trade route linkage, and optimised monthly SQL pipelines in Databricks supporting high-priority datasets across multiple teams.}
                \item {Established comprehensive data quality frameworks using Great Expectations for automated monitoring and led quality assurance negotiations with external providers, strengthening the department's contract position following data integrity issues.}
                % \item {Maintained and optimised a monthly SQL pipeline in Databricks, supporting a high-priority shipping trade dataset used across multiple teams.}
                % \item {Implemented a data quality assurance framework using Great Expectations, enabling monthly automated monitoring of key datasets and early detection of anomalies.}
                % \item {Directed quality assurance efforts with an external data provider, initiating improvements after data quality issues and strengthening the department’s position in contract renegotiations.}
              \end{itemize}}  
      \end{cvitems}
    }    

%--------------------------------------------------------- 
  \cventry
    {Office for National Statistics} % Job title
    {Data Scientist} % Organization
    {Newport, UK} % Location
    {Nov. 2022 - Apr. 2024} % Date(s)
    {\renewcommand{\labelitemii}{\bullet}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[] {\jobstyle{} 
            \begin{itemize} % Description(s) of tasks/responsibilities
                \item {Transformed manual workflows into production-grade systems for a high-profile weekly economic bulletin, developing modular Python pipelines that improved processing speed by 80\%+ through automation of Excel-based processes, with robust validation and seasonal adjustment (TRAMO-SEATS) for high-frequency time series.}
                \item {Enabled economist decision-making by building PowerBI dashboards for rapid insight extraction and providing technical support to domain experts in a fast-paced release environment, ensuring timely delivery of economic indicators.}
                \item{Advanced team capabilities through mentoring junior analysts in Python and PowerBI, implementing GitLab documentation standards and internal workshops, and pioneering LLM-based automation (RAG) for publication workflows, establishing best practices in version control, modular code design, and testing.}
                % \item {Built PowerBI dashboards that enabled economists to extract timely insights, supporting rapid analysis and decision-making in a fast-paced environment.}
                % \item {Applied TRAMO-SEATS for seasonal adjustment of high-frequency time series, improving the accuracy of economic indicators.}
                % \item {Led innovation in statistical automation by implementing LLM-based text generation and Retrieval-Augmented Generation (RAG), streamlining publication workflows.}
                % \item {Spearheaded GitLab documentation and internal workshops, enhancing team onboarding and knowledge transfer.}
              \end{itemize}}  
      \end{cvitems}
    }        

%---------------------------------------------------------
  \cventry
    {Cardiff University (CUBRIC)} % Job title
    {Researcher (PhD Candidate)} % Organization
    {Cardiff, UK} % Location
    {Oct. 2018 - Mar. 2023} % Date(s)
    {\renewcommand{\labelitemii}{\bullet}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[] {\jobstyle{} 
            \begin{itemize} % Description(s) of tasks/responsibilities
            \item {Led end-to-end research projects investigating rhythmic brain activity in motor performance, managing the complete scientific lifecycle from literature review and ethical approval through experimental design (Python/PsychoPy), participant recruitment, and peer-reviewed publication at international conferences.}
            \item {Delivered advanced analytical insights through signal processing and time-frequency analysis of neural data (ICA, wavelet transforms), applying rigorous statistical methods (ANOVA, regression, permutation tests) in MATLAB and R to validate hypotheses and extract meaningful patterns from complex datasets.}
            \item {Scaled computational workflows by optimizing high-throughput data processing on SLURM clusters for large-scale datasets, demonstrating ability to handle computationally intensive analysis and manage data pipelines efficiently.}
            % \item {Performed rigorous statistical testing using MATLAB and R, including correlation, regression, ANOVA, and permutation tests to validate hypotheses.}
            % \item {Managed high-throughput data processing on SLURM clusters, optimising computational workflows for large datasets.}
            % \item {Published findings in peer-reviewed journals and presented at international conferences, contributing to the field of cognitive neuroscience.}
              \end{itemize}}  
       \end{cvitems}
    }
\end{cventries}
